Identification of protoneutron star g-modes in gravitational-wave data

### 2020-07-07 simulations.tex
more updates
Added a short description of the simulations in section II with a table of the 2d models and a few new references.

\section{Core collapse supernova simulations}

@@

>>>>

\section{Core collapse supernova simulations}
\label{sec:simulations}

@@

\maob{%%
  We apply our analysis to a set of 25 spherically symmetric
  \citep{Torres:2019} and 7 two-dimensional axisymmetric models of
  stellar core collapse simulated with two codes, CoCoNuT
  (one-dimensional models) and AENUS-ALCAR
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
  (one- and two-dimensional models).  CoCoNuT
  \citep{Cerda-Duran__2008__AA__GRMHD-code} is a code for general
  relativistic hydrodynamics coupled to the Fast Multigroup Transport
  scheme \citep{Mueller_Janka_2015_FMT} providing an approximate
  description of the emission and transport of neutrinos.  AENUS-ALCAR
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
  combines special relativistic (magneto-)hydrodynamics, a modified
  Newtonian gravitational potential approximating the effects of
  general relativity \citep{Marek_etal__2006__AA__TOV-potential}, and
  a spectral two-moment neutrino transport solver
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}.
  We included the relevant reactions between matter and neutrinos of
  all flavours, i.e., emission and absorption by nucleons and nuclei,
  electron-positron pair annihilation, nucleonic bremsstrahlung, and
  scattering off nucleons, nuclei, and electrons.
  %%
}

\maob{%%
  Our spherically symmetric simulations cover the range of initial
  stellar masses $M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$.  They were
  carried out using six equations of state (EOSs).  They are
  complemented by a set of two-dimensional axisymmetric models
  consisting of stellar core collapse of five stars with zero-age
  main-sequence masses of $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
  evolved through the hydrostatic phases by
  \cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
  We performed one simulation of each stellar model using the equation
  of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS}
  with an incompressibility of $K = 220 \, \mathrm{MeV}$ and added
  comparison models with the SFHo EOS
  \cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
  and the EOS of
  \cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
  for the one with $M_{\mathrm{ZAMS}} = 15 \, \Msol$ (see Table
  \ref{Tab:2dSimList} for a list of models).
  %%
}

\maob{%%
  We mapped the pre-collapse state of the stars to a spherical
  coordinate system with $n_r = 400$ zones in radial direction
  distributed logarithmically with a minimum grid width of $(\Delta
  r)_{\mathrm{min}} = 400 \, \mathrm{m}$ and an outer radius of
  $r_{\mathrm{max}} = 8.3 \times 10^{9} \, \mathrm{cm}$ and 
  $n_{\theta} = 128$ equidistant cells in angular direction.  For the
  neutrino energies, we used a logarithmic grid with $n_e = 10$
  bins up to $240 \, \mathrm{MeV}$.
  %%
}

\maob{%%
  All spherical and most axisymmetric models fail to achieve shock
  revival during the time of our simulations.  Only the two stars with
  the highest masses, \texttt{s25} and \texttt{s40}, develop
  relatively late explosions in axisymmetry.  Consequently, mass
  accretion onto the PNSs proceeds at high rates for a long time in
  all cases and causes them to oscillate with their characteristic
  frequencies.  The final masses of the PNSs are in the range of
  $M_{\mathrm{PNS}} = 1.47 - 2.33 \, \Msol$, i.e., insufficient for
  producing a black hole.
  %%
}

\begin{table}
  \centering
  \begin{tabular}{c|cc|ccc}
    \hline
    Simulation & $M_\mathrm{ZAMS} [\Msol]$ & EOS & $t_{\mathrm{f}} [\mathrm{s}]$&
    explosion & $M_{\mathrm{PNS}} [\Msol]$
    \\ 
    \hline
    \texttt{s11} & 11.2 & LS220 & 1.86 & $\times$ &  1.47
    \\ 
    \texttt{s15} & 15.0 & LS220 & 1.66 & $\times$ &  2.00
    \\ 
    \texttt{s15S} & 15.0 & SFHo & 1.75 & $\times$ &  2.02
    \\ 
    \texttt{s15G} & 15.0 & GShen & 0.97 & $\times$ &  1.86
    \\ 
    \texttt{s20} & 20.0 & LS220 & 1.53 & $\times$ & 1.75
    \\ 
    \texttt{s25} & 25.0 & LS220 & 1.60 & $0.91$ &  2.33
    \\ 
    \texttt{s40} & 40.0 & LS220 & 1.70 & $1.52$ &  2.23
    \\ \hline
  \end{tabular}
  \caption{%%
    List of axisymmetric simulations.  We present the name of the models, the initial
    mass of the progenitors, and the EOS used, and the  final
    post-bounce time of the simulations.  For models which explode,
    we list the time at which the shock starts to expand in column
    ``explosion''; otherwise, a $\times$ sign is displayed.  The final
    column indicates the mass of the PNS at the end of the
    simulation.  
    %%
  }
  \label{Tab:2dSimList}
\end{table}

%%% Local Variables:
%%% TeX-master: "ccsn"
%%% End:
